\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2018-06-08 doc/USER_MANUAL/11_graphics.tex
reverted the change made yesterday for the VTK executable. It turns out there was no bug, it was just the users manual that was saying something wrong (i.e. obsolete).

At the beginning of the source file \texttt{src/auxiliaries/combine\_vol\_data\_impl.f90} there is a logical parameter \texttt{USE\_VTK\_INSTEAD\_OF\_MESH},
whose default value is \texttt{.false.}, which can be used to generate the combined output file directly in VTK format, which can then be visualized using Paraview.

If the value of this parameter is \texttt{.false.}, the output mesh file will have a name of the form \texttt{velocity\_Z\_it000400.mesh}.
One then has to convert the \texttt{.mesh} file into the VTU (Unstructured grid file) format which can be viewed in ParaView.

>>>>

When compiling the code, you will get two executables related to this: xcombine\_vol\_data, and xcombine\_vol\_data\_vtk.
Use the executable that has the \_vtk extension if you want to directly create VTK files.
If you use the executable that does not have the \_vtk extension, then the output mesh file will have a name of the form \texttt{velocity\_Z\_it000400.mesh}.
You will then have to convert the \texttt{.mesh} file into the VTU (Unstructured grid file) format which can be viewed in ParaView.
